\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{float}
\usepackage[left=0.25in,right=0.25in,top=0.25in,bottom=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}


\begin{document}
   \pagenumbering{gobble}

   % heading info
   \begin{center}
      Saeed Rahaman\\
      Phone: 321-525-062\\
      Email: srahaman@knights.ucf.edu\\
      Website: https://saeedrahaman.herokuapp.com/ \\
   \end{center}

   % EDUCATION INFO

   \noindent\underline{\textbf{Education}}
   \vspace{0.25cm}

   \begin{minipage}{0.95\textwidth}
      Master of Science, \textbf{University of Central Florida} \hfill \textbf{January 2019 - December 2021}

      \vspace{-0.25cm}
      
      \begin{itemize}\setlength\itemsep{-0.2cm}
         \item Recently graduated with a master’s in computer engineering with coursework focused on artificial intelligence.
         \item Studied machine learning, natural language processing, and computer vision techniques and applications.
         \item Gained experience with machine learning libraries such as TensorFlow, PyTorch, NumPy, and Pandas.
      \end{itemize}

      Bachelor of Science, \textbf{University of Central Florida} \hfill \textbf{December 2018}

      \vspace{-0.25cm}

      \begin{itemize}\setlength\itemsep{-0.2cm}
         \item Graduated from University of Central Florida with a Bachelor of Science in Electrical Engineering.
         \item Gained experience giving lectures and presentations in front of committees.
         \item Developed teamwork and leadership skills throughout multiple class projects.
         \item Experience working in a lab environment.
      \end{itemize}
   \end{minipage}


   % PROJECT INFO

   \vspace{0.5cm}
   \noindent\underline{\textbf{Major Projects}}

   \begin{minipage}{0.95\textwidth}
      \vspace{0.25cm}
      \begin{itemize}
         \item \textbf{Interactive Chess Trainer}
            \vspace{-0.4cm}

            \begin{itemize}
               \item Smart chess board for senior design degree requirement project.
               \vspace{-0.1cm}

               \begin{itemize}\setlength\itemsep{-0.05cm}
                  \item Lead a group to research, design, develop, and build a smart chess board. 
                  \item Responsible for researching hardware components and developing multiple design strategies.
                  \item Built working PCB microcontroller from design strategy using EasyEDA.
                  \item Developed basic AI software to allow interactive playing experience.
               \end{itemize}

            \end{itemize}

         \item \textbf{Facial Recognition Software}
            \vspace{-0.4cm}

            \begin{itemize}\setlength\itemsep{-0.5cm}
               \item Worked in a group to design a facial recognition software using a neural network.
               \vspace{-0.1cm}

               \begin{itemize}\setlength\itemsep{-0.05cm}
                  \item Responsible for design strategies to accomplish objectives.
                  \item Designed a custom neural network and trained the model several datasets.
                  \item Achieved 88\% accuracy at detecting faces in camera view.
               \end{itemize}

            \end{itemize}

      \item \textbf{Drug Resistance In Tuberculosis}
         \vspace{-0.4cm}

         \begin{itemize}\setlength\itemsep{-0.5cm}
            \item Worked on project to predict drug resistance of Tuberculosis.
            \vspace{-0.1cm}

            \begin{itemize}\setlength\itemsep{-0.05cm}
               \item Researched and implemented various machine learning techniques.
               \item Gathered and preprocessed gigabytes of data for training and testing.
               \item Utilized feature engineering techniques to classify data by mutations.
               \item 85\% accuracy in predicting whether a strain of Tuberculosis was drug resistant.
            \end{itemize}

         \end{itemize}

         \item \textbf{BERT-to-BART Summarization}
         \vspace{-0.4cm}

         \begin{itemize}\setlength\itemsep{-0.5cm}
            \item Utilized extractive and abstractive NLP techniques to summarize biological research paeprs.
            \vspace{-0.1cm}

            \begin{itemize}\setlength\itemsep{-0.05cm}
               \item Created new embeddings using Word2Vec, TF-IDF scores, and SBERT.
               \item Implemented ensemble of clustering algorithms to find the best embeddings.
               \item Designed a pipeline to send embeddings to the BART model for abstractive summarization.
               \item Achieved a ROUGE-2 score 3\% lower than several state-of-the-art models.
            \end{itemize}

         \end{itemize}

      \end{itemize}
      
   \end{minipage}

   % EXPERIENCE INFO

   \vspace{0.5cm}
   \noindent\underline{\textbf{Relevant Experience}}
   \vspace{0.25cm}

   \begin{minipage}{0.95\textwidth}
      \textbf{Freelance Tutor} \hfill \textbf{2016-2022}

      \vspace{-0.25cm}

      \begin{itemize}\setlength\itemsep{-0.2cm}
         \item Helped students improve their understanding of concepts in math, chemistry, and computer science.
         \item Increased students' performance by 1-2 letter grade(s).
   
      \end{itemize}

   \end{minipage}


   % SKILLS SECTION

   \vspace{0.5cm}
   \noindent\underline{\textbf{Skills}}\\
   \vspace{-0.25cm}

   \begin{minipage}{0.95\textwidth}
      \vspace{-0.75cm}

      \begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
         
         \begin{itemize}\setlength\itemsep{-0.15cm}
            \setlength{\itemindent}{-0.5em}
            \item Proficient in Python, C, JavaScript, and Matlab
            \item Experience working in a Linux environment
         \end{itemize}
         & 
         \begin{itemize}\setlength\itemsep{-0.15cm}
            \setlength{\itemindent}{-0.5em}
            \item Experience with data mining and feature engineering
            \item Programming experience on microcontrollers
         \end{itemize}
     
        \end{tabular}
   \end{minipage}
   

\end{document}
% end file